---
fontsize: 22pt
output:
  word_document: default
font-family: Arial
theme: united
title: '**Comorbidity between mood and anxiety disorders: a systematic review and meta-analysis **'
---
<hr>
<br>

<style>
  
#TOC {
 position: fixed;
  left: 0;
  top: 0;
  width: 280px;
  height: 100%;
  overflow:auto;
}
body {
  max-width: 1200px;
  margin: auto;
  margin-left:150px;
  line-height: 20px;
}
h1.title {
    font-size: 28px;
}
h4 {
    font-size: 15px;
}
h3 {
    font-size: 16px;
}
h2 {
    font-size: 20px;
}
h1 {
    font-size: 24px;
}
.center {
    display: block;
    margin-left: auto;
    margin-right: auto;
    width: 28%;
}
.table {
    width: 40%;
}
</style>

\vspace{20mm}

<br>
<br>
**Author:** Carmen Lim \newline{}
<br>
<br>
**Report date:** 28 May 2020
<br>
<br>
<br>
<br>
<br>
<br>
\newpage
 
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries, include = FALSE}
library(Matrix)
library(metafor)
library(ggplot2)
library(plotly)
library(here)
library(dplyr)
library(tinytex)
```

```{r readdata, echo = FALSE}
ma <- read.csv(here("data", "ma3.csv"))
ma$R_UnadjRate1 <- as.numeric(ma$R_UnadjRate1)  
```

```{r function, echo = FALSE}

unadj_fn <- function(y2,z ){
dat2 <- escalc(measure="OR", ai=a, bi=b, ci=c, di=d, data=ma1)
dat2$yi <- replmiss(dat2$yi, log(dat2$R_UnadjRate1))
dat2$zi <-sign(dat2$yi)*qnorm(dat2$R_PValue_Unadjusted/2, lower.tail = FALSE)
dat2$sei <- dat2$yi/dat2$zi
dat2$sei <- replmiss(dat2$sei, with(dat2, (log(R_UnadjUpperCI1) - log(R_UnadjLowerCI1))/(2*1.96)))
dat2$vi <- replmiss(dat2$vi, dat2$sei^2)
dat2$zi <- dat2$sei <-NULL
res2 <- rma(yi, vi, slab=paste(author_year,",",country),   data=dat2)
taf <- trimfill(res2)
forest(res2,atransf=exp, xlab="Unadjusted Odds Ratio" , cex = 0.6, xlim=c(-10, 10),  mlab="", at=log(c(0.01, 1, 5, 10, 25, 50, z)), psize=1.4,order=order(res2$yi))
par(font=2)
text(-10,   nrow(ma1)+1.5, cex = 0.6, "Study",  pos=4)
text(10,    nrow(ma1)+1.5, cex = 0.6, "Unadjusted Odds Ratio [95% CI]", pos=2)
text(-10, y2, pos=4,  cex = 0.6, bquote(paste("Heterogeneity (Q = ", .(formatC(res2$QE, digits=2, format="f")), ", df = ", .(res2$k - res2$p),", p = ", .(formatC(res2$QEp, digits=2, format="f")), "; ", I^2, " = ",
.(formatC(res2$I2, digits=1, format="f")), "%)")))

funnel(taf, legend=TRUE)
regtest(res2, model="rma") 
}


adj_fn <- function(y2,z ){
dat2 <- escalc(measure="OR", ai=a, bi=b, ci=c, di=d, data=ma2)
dat2$yi <- replmiss(dat2$yi, log(dat2$R_AdjRate1))
dat2$zi <-sign(dat2$yi)*qnorm(dat2$R_PValue_Adjusted/2, lower.tail = FALSE)
dat2$sei <- dat2$yi/dat2$zi
dat2$sei <- replmiss(dat2$sei, with(dat2, (log(R_AdjUpperCI1) - log(R_AdjLowerCI1))/(2*1.96)))
dat2$vi <- replmiss(dat2$vi, dat2$sei^2)
dat2$zi <- dat2$sei <-NULL
res2 <- rma(yi, vi, slab=paste(author_year, ",",country),   data=dat2)
taf <- trimfill(res2)
forest(res2,atransf=exp, xlab="Adjusted Odds Ratio" ,cex=0.6, xlim=c(-10, 10), mlab="", at=log(c(0.01, 1, 2, 5,10,50, z)), psize=1.4,order=order(res2$yi))
par(font=2)
text(-10,  nrow(ma2)+1.5, cex = 0.6, "Study",  pos=4)
text(10,   nrow(ma2)+1.5, cex = 0.6, "Adjusted Odds Ratio [95% CI]", pos=2)
text(-10, y2, pos=4, cex=0.6, bquote(paste("Heterogeneity (Q = ",
                                      .(formatC(res2$QE, digits=2, format="f")), ", df = ", .(res2$k - res2$p),
                                      ", p = ", .(formatC(res2$QEp, digits=2, format="f")), "; ", I^2, " = ",
                                      .(formatC(res2$I2, digits=1, format="f")), "%)")))
funnel(taf, legend=TRUE)
regtest(res2, model="rma") 
}
```

#   Table 2.Broadly-defined mood disorder and anxiety disorders
<br>
<br>
<br>
<br>

##  Lifetime estimates
<br>
<br>

### Mood and GAD [unadjusted] 


```{r mood_gad, echo = FALSE  }
#ma1 <- ma %>% filter(mood_gad_unadj == 1 & temporality == "lifetime")
#unadj_fn(-1, 100)
```
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Mood and GAD [adjusted] 

```{r mood_gad2, echo = FALSE}
#ma2 <- ma %>% filter(mood_gad_adj == 1 & temporality == #"lifetime")
#adj_fn(-1, 100)
```

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Mood and Social Phobia [unadjusted] 

```{r mood_so, echo = FALSE , dpi=300 }
ma1 <- ma %>% filter(mood_so_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 50) 
```

### Mood and Social Phobia [adjusted] 

```{r mood_so2, echo = FALSE}
#ma2 <- ma %>% filter(mood_so_adj == 1 & temporality == #"lifetime")
#adj_fn(-1, 100)
```

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Mood and Specific Phobia [unadjusted] 

```{r mood_sp, echo = FALSE }
ma1 <- ma %>% filter(mood_sp_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 10) 
```

### Mood and Specific Phobia [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Mood and Anxiety disorder [unadjusted] 

```{r mood_anx, echo = FALSE}
ma1 <- ma %>% filter(mood_anx_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 100) 
```

### Mood and Anxiety disorder [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

##  Period-prevalence estimates
<br>
<br>


### Mood and GAD [unadjusted] 
```{r mood_gad1, echo = FALSE  }
#ma1 <- ma %>% filter(mood_gad_unadj == 1 & temporality == "period-prevalence")
#unadj_fn(-1, 100)
```
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Mood and GAD [adjusted] 
```{r mood_gad3, echo = FALSE}
ma2 <- ma %>% filter(mood_gad_adj == 1 & temporality == "period-prevalence")
adj_fn(-1, 150)
```

### Mood and Social Phobia [unadjusted] 
```{r mood_so1, echo = FALSE  }
ma1 <- ma %>% filter(mood_so_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 50) 
```

### Mood and Social Phobia [adjusted] 
```{r mood_so3, echo = FALSE}
ma2 <- ma %>% filter(mood_so_adj == 1 & temporality == "period-prevalence")
adj_fn(-1, 100)
```

### Mood and Specific Phobia [unadjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Mood and Specific Phobia [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Mood and Anxiety disorder [unadjusted] 

```{r mood_anx1, echo = FALSE}
ma1 <- ma %>% filter(mood_anx_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 100) 
```

### Mood and Anxiety disorder [adjusted] 

```{r mood_anx3, echo = FALSE}
ma2 <- ma %>% filter(mood_anx_adj == 1 & temporality == "period-prevalence")
adj_fn(-1, 100)
```

<br>
<br>
<br>
<br>

#   Table 3.Broadly-defined depressive disorder (DEP) and anxiety disorders
<br>
<br>
<br>
<br>

##  Lifetime estimates
<br>
<br>

### DEP and Agoraphobia [unadjusted] 

```{r dep_ago, echo = FALSE  }
ma1 <- ma %>% filter(dep_ago_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 150) 
```

### DEP and Agoraphobia [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DEP and OCD [unadjusted] 
 
```{r dep_ocd, echo = FALSE  }
ma1 <- ma %>% filter(dep_ocd_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 150) 
```

### DEP and OCD [adjusted] 
```{r dep_ocd1, echo = FALSE  }
ma2 <- ma %>% filter(dep_ocd_adj == 1 & temporality == "lifetime")
adj_fn(-1, 150)
```


### DEP and GAD [unadjusted] 
```{r dep_gad, echo = FALSE  }
ma1 <- ma %>% filter(dep_gad_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 300) 
```

### DEP and GAD [adjusted] 
```{r dep_gad1, echo = FALSE  }
ma2 <- ma %>% filter(dep_gad_adj == 1 & temporality == "lifetime")
adj_fn( -1, 300)
```

### DEP and Panic disorder [unadjusted]   
```{r dep_pds, echo = FALSE  }
ma1 <- ma %>% filter(dep_pds_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 300) 
```

### DEP and Panic disorder [adjusted]  
```{r dep_pds1, echo = FALSE  }
ma2 <- ma %>% filter(dep_pds_adj == 1 & temporality == "lifetime")
adj_fn(-1, 100)
```

### DEP and PTSD [unadjusted]  

```{r dep_pts, echo = FALSE  }
ma1 <- ma %>% filter(dep_pts_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 250) 
```

### DEP and PTSD [adjusted]  
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DEP and Social phobia [unadjusted]   
```{r dep_so, echo = FALSE  }
ma1 <- ma %>% filter(dep_so_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 50) 
```

### DEP and Social phobia [adjusted]
```{r dep_so1, echo = FALSE  }
ma2 <- ma %>% filter(dep_so_adj == 1 & temporality == "lifetime")
adj_fn( -1, 10)
```

### DEP and Specific phobia [unadjusted]   
  
```{r dep_sp, echo = FALSE  }
ma1 <- ma %>% filter(dep_sp_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 50) 
```

### DEP and Specific phobia [adjusted]   
```{r dep_sp1, echo = FALSE  }
ma2 <- ma %>% filter(dep_sp_adj == 1 & temporality == "lifetime")
adj_fn( -1, 10)
```

### DEP and Anxiety disorder [unadjusted]   
```{r dep_anx, echo = FALSE  }
ma1 <- ma %>% filter(dep_anx_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 1000) 
```


### DEP and Anxiety disorder [adjusted]    
```{r dep_anx1, echo = FALSE  }
ma2 <- ma %>% filter(dep_anx_adj == 1 & temporality == "lifetime")
adj_fn(-1, 1000) 
```


##  Period-prevalence estimates
<br>
<br>

### DEP and Agoraphobia [unadjusted] 

```{r dep_ago1, echo = FALSE  }
ma1 <- ma %>% filter(dep_ago_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 150)
```  

### DEP and Agoraphobia [adjusted] 
```{r dep_ago2, echo = FALSE  }
ma2 <- ma %>% filter(dep_ago_adj == 1 & temporality == "period-prevalence")
adj_fn( -1, 50)
```  


### DEP and OCD [unadjusted] 
  
```{r dep_ocd2, echo = FALSE  }
ma1 <- ma %>% filter(dep_ocd_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 150) 
```

### DEP and OCD [adjusted] 

```{r dep_ocd3, echo = FALSE  }
ma2 <- ma %>% filter(dep_ocd_adj == 1 & temporality == "period-prevalence")
adj_fn(-1, 150)
```
 
### DEP and GAD [unadjusted] 
  
```{r dep_gad2, echo = FALSE  }
ma1 <- ma %>% filter(dep_gad_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 300) 
```

### DEP and GAD [adjusted] 
```{r dep_gad3, echo = FALSE  }
ma2 <- ma %>% filter(dep_gad_adj == 1 & temporality == "period-prevalence")
adj_fn( -1, 300)
```
 
### DEP and Panic disorder [unadjusted] 

```{r dep_pds2, echo = FALSE  }
ma1 <- ma %>% filter(dep_pds_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 300) 
```

### DEP and Panic disorder [adjusted] 
```{r dep_pds3, echo = FALSE  }
ma2 <- ma %>% filter(dep_pds_adj == 1 & temporality == "period-prevalence")
adj_fn(-1, 100)
```

### DEP and PTSD [unadjusted] 

```{r dep_pts1, echo = FALSE  }
ma1 <- ma %>% filter(dep_pts_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 250) 
```

### DEP and PTSD [adjusted] 
```{r dep_pts2, echo = FALSE  }
ma2 <- ma %>% filter(dep_pts_adj == 1 & temporality == "period-prevalence")
adj_fn( -1, 100)
```

### DEP and Social phobia [unadjusted] 

```{r dep_so2, echo = FALSE  }
ma1 <- ma %>% filter(dep_so_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 100) 
```

### DEP and Social phobia [adjusted] 
```{r dep_so3, echo = FALSE  }
ma2 <- ma %>% filter(dep_so_adj == 1 & temporality == "period-prevalence")
adj_fn( -1, 100)
```


### DEP and Specific phobia [unadjusted] 

```{r dep_sp2, echo = FALSE  }
ma1 <- ma %>% filter(dep_sp_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 50) 
```

### DEP and Specific phobia [adjusted] 
```{r dep_sp3, echo = FALSE  }
ma2 <- ma %>% filter(dep_sp_adj == 1 & temporality == "period-prevalence")
adj_fn( -1, 10)
```

### DEP and Anxiety disorder [unadjusted] 
  
```{r dep_anx2, echo = FALSE  }
ma1 <- ma %>% filter(dep_anx_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-2, 900)
```

### DEP and Anxiety disorder [adjusted] 
```{r dep_anx3, echo = FALSE  }
ma2 <- ma %>% filter(dep_anx_adj == 1 & temporality == "period-prevalence")
adj_fn(-1, 150)
```

# Table 4. Broadly-defined dysthymic disorder (DYS) and anxiety disorders
<br>
<br>
<br>
<br>

##  Lifetime estimates
<br>
<br>

### DYS and Agoraphobia [unadjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and Agoraphobia [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and OCD [unadjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and OCD [adjusted] 
```{r dys_ocd, echo = FALSE  }
ma1 <- ma %>% filter(dys_ocd_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 150) 
```
 
### DYS and GAD [unadjusted] 
```{r dys_gad, echo = FALSE  }
ma1 <- ma %>% filter(dys_gad_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 600) 
```

### DYS and GAD [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and Panic disorder [unadjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and Panic disorder [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and PTSD [unadjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and PTSD [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and Social phobia [unadjusted] 
```{r dys_so, echo = FALSE  }
ma1 <- ma %>% filter(dys_so_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 200) 
```

### DYS and Social phobia [adjusted] 
```{r dys_so1, echo = FALSE  }
ma2 <- ma %>% filter(dys_so_adj == 1 & temporality == "lifetime")
adj_fn(-1, 100)
```


### DYS and Specific phobia [unadjusted] 

```{r dys_sp, echo = FALSE  }
ma1 <- ma %>% filter(dys_sp_unadj == 1 & temporality == "lifetime")
unadj_fn(-1, 100)  
```


### DYS and Specific phobia [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and Anxiety disorder [unadjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and Anxiety disorder [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

##  Period-prevalence estimates
<br>
<br>

### DYS and Agoraphobia [unadjusted] 
  

```{r dys_ago, echo = FALSE  }
ma1 <- ma %>% filter(dys_ago_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 100)  
```

### DYS and Agoraphobia [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>


### DYS and OCD [unadjusted] 
  
```{r dys_ocd1, echo = FALSE  }
ma1 <- ma %>% filter(dys_ocd_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 600) 
```

### DYS and OCD [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and GAD [unadjusted] 

```{r dys_gad1, echo = FALSE  }
ma1 <- ma %>% filter(dys_gad_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 600) 
```

### DYS and GAD [adjusted] 
```{r dys_gad2, echo = FALSE  }
ma2 <- ma %>% filter(dys_gad_adj == 1 & temporality == "period-prevalence")
adj_fn(-1, 100)
```

### DYS and Panic disorder [unadjusted] 
```{r dys_pds, echo = FALSE  }
ma1 <- ma %>% filter(dys_pds_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 150) 
```

### DYS and Panic disorder [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and PTSD [unadjusted] 

```{r dys_pts, echo = FALSE  }
ma1 <- ma %>% filter(dys_pts_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 200) 
```

### DYS and PTSD [adjusted] 
```{r dys_pts1, echo = FALSE  }
ma2 <- ma %>% filter(dys_pts_adj == 1 & temporality == "period-prevalence")
adj_fn(-1, 100)
```

### DYS and Social phobia [unadjusted] 

```{r dys_so2, echo = FALSE  }
ma1 <- ma %>% filter(dys_so_unadj == 1 & temporality == "period-prevalence")
unadj_fn(-1, 200) 
```

### DYS and Social phobia [adjusted] 
```{r dys_so3, echo = FALSE  }
ma2 <- ma %>% filter(dys_so_adj == 1 & temporality == "period-prevalence")
adj_fn(-1, 100)
```


### DYS and Specific phobia [unadjusted] 
  
```{r dys_sp1, echo = FALSE  }
ma1 <- ma %>% filter(dys_sp_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 250)
```

### DYS and Specific phobia [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and Anxiety disorder [unadjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### DYS and Anxiety disorder [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

# Table 5. Broadly-defined bipolar disorder (BIPOLAR) and anxiety disorders
<br>
<br>
<br>
<br>

##  Lifetime estimates
<br>
<br>

### Bipolar and Agoraphobia [unadjusted] 


```{r bi_ago, echo = FALSE  }
ma1 <- ma %>% filter(bi3_ago_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 200) 
```

### Bipolar and Agoraphobia [adjusted] 

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Bipolar and OCD [unadjusted] 
 
```{r bi_ocd, echo = FALSE  }
ma1 <- ma %>% filter(bi3_ocd_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 300) 
```

### Bipolar and OCD [adjusted]  
```{r bi_ocd1, echo = FALSE  }
ma2 <- ma %>% filter(bi3_ocd_adj == 1 & temporality == "lifetime")
adj_fn( -1, 100)
```



### Bipolar and GAD [unadjusted] 
 
```{r bi_gad, echo = FALSE  }
ma1 <- ma %>% filter(bi3_gad_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 150) 
```

### Bipolar and GAD [adjusted]   
```{r bi_gad1, echo = FALSE  }
ma2 <- ma %>% filter(bi3_gad_adj == 1 & temporality == "lifetime")
adj_fn( -1, 100)
```



### Bipolar and Panic disorder [unadjusted] 
 
```{r bi_PD, echo = FALSE  }
ma1 <- ma %>% filter(bi3_pd_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 150) 
```

### Bipolar and Panic disorder [adjusted] 
```{r bi_PD1, echo = FALSE  }
ma2 <- ma %>% filter(bi3_pd_adj == 1 & temporality == "lifetime")
adj_fn( -1, 100)
```


### Bipolar and PTSD [unadjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Bipolar and PTSD [adjusted] 

```{r bi_pts1, echo = FALSE  }
ma2 <- ma %>% filter(bi3_pts_adj == 1 & temporality == "lifetime")
adj_fn( -1, 10)
```
 
### Bipolar and Social phobia [unadjusted] 

```{r bi_so, echo = FALSE  }
ma1 <- ma %>% filter(bi3_so_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 50) 
```

### Bipolar and Social phobia [adjusted] 
```{r bi_so1, echo = FALSE  }
ma2 <- ma %>% filter(bi3_so_adj == 1 & temporality == "lifetime")
adj_fn( -1, 10)
```

 
### Bipolar and Specific phobia [unadjusted] 
```{r bi_sp, echo = FALSE  }
ma1 <- ma %>% filter(bi3_sp_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 50) 
```

### Bipolar and Specific phobia [adjusted] 
```{r bi_sp1, echo = FALSE  }
ma2 <- ma %>% filter(bi3_sp_adj == 1 & temporality == "lifetime")
adj_fn( -1, 10)
```

### Bipolar and Anxiety disorder [unadjusted] 
```{r bi_anx, echo = FALSE  }
ma1 <- ma %>% filter(bi3_anx_unadj == 1 & temporality == "lifetime")
unadj_fn( -1, 200) 
```

### Bipolar and Anxiety disorder [adjusted] 
```{r bi_anx1, echo = FALSE  }
ma2 <- ma %>% filter(bi3_anx_adj == 1 & temporality == "lifetime")
adj_fn(-1, 20)
```

##  Period-prevalence estimates
<br>
<br>

### Bipolar and Agoraphobia [unadjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Bipolar and Agoraphobia [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Bipolar and OCD [unadjusted] 

```{r bi_ocd2, echo = FALSE  }
ma1 <- ma %>% filter(bi3_ocd_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 150) 
```

### Bipolar and OCD [adjusted] 
```{r bi_ocd3, echo = FALSE  }
ma2 <- ma %>% filter(bi3_ocd_adj == 1 & temporality == "period-prevalence")
adj_fn( -1, 100)
```

### Bipolar and GAD [unadjusted] 

```{r bi_gad2, echo = FALSE  }
ma1 <- ma %>% filter(bi3_gad_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 150) 
```

### Bipolar and GAD [adjusted] 
```{r bi_gad3, echo = FALSE  }
ma2 <- ma %>% filter(bi3_gad_adj == 1 & temporality == "period-prevalence")
adj_fn( -1, 100)
```

### Bipolar and Panic disorder [unadjusted] 

```{r bi_PD2, echo = FALSE  }
ma1 <- ma %>% filter(bi3_pd_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 150) 
```

### Bipolar and Panic disorder [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Bipolar and PTSD [unadjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Bipolar and PTSD [adjusted] 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Bipolar and Social phobia [unadjusted] 

```{r bi_so2, echo = FALSE  }
ma1 <- ma %>% filter(bi3_so_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 50) 
```

### Bipolar and Social phobia [adjusted] 

```{r bi_so3, echo = FALSE  }
ma2 <- ma %>% filter(bi3_so_adj == 1 & temporality == "period-prevalence")
adj_fn( -1, 10)
```

### Bipolar and Specific phobia [unadjusted]
```{r bi_sp2, echo = FALSE  }
ma1 <- ma %>% filter(bi3_sp_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 50) 
```

### Bipolar and Specific phobia [adjusted]
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

### Bipolar and Anxiety disorder [unadjusted]
```{r bi_anx2, echo = FALSE  }
ma1 <- ma %>% filter(bi3_anx_unadj == 1 & temporality == "period-prevalence")
unadj_fn( -1, 200) 
```

### Bipolar and Anxiety disorder [unadjusted]